MCTS Applied to Co-operative Problems

### 2015-08-04 Report/response.tex

\paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
Have rewritten this to point out that MCTS can't provide anything but random if it isn't given enough time or depth to search to a state that provides a reward.
\paragraph*{\textit{The research problem is stated, but should be stated more clearly in the Introduction.}}
Added at the beginning of the introduction a clear statement of the research problem.

@@

\paragraph*{\textit{The list of references is short (four) and does not include any references to work on cooperative agents, swarm behaviour, etc.}}
\paragraph*{\textit{Despite these concerns with the presentation, I liked the idea and the authors' approach to investigating the problem. The paper could be improved greatly with a little bit of work.}}
\subsection{Review 3 (Reviewer G)}
\paragraph*{\textit{The agents move simultaneously or alternately?}}
Added a section to highlight this.

@@

We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
\paragraph*{\textit{If an agent reaches a goal, is it known to the other agents?}}
We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.

\paragraph*{\textit{In what sense this domain interesting compared to other domains?}}

\paragraph*{\textit{Is the problem domain a real time problem? How long is a tick? 40ms? Do all agents return an action within a tick? Possible 5 actions mean up, down left, right and stay where it is?}}
The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.

\paragraph*{\textit{What is "Uniform Cost applied to Trees"? Is it something similar to the famous "Upper Confidence bound applied to Trees"? If not, please cite something.}}
We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.
\paragraph*{\textit{About MCTS, what are "iteration", "UCT Border", and "rollout border"?
My guess is iteration means the number of rollouts,
UCT border means the UCT tree search depth limit, and
rollout border means the length of the sequence of rollout.
Am I correct?
These phrases are different from normal terminology used in MCTS.}}
\paragraph*{\textit{What is the reward of the rollout? Maybe the raw score?}}
\paragraph*{\textit{About the results, what is averaged?
How many runs are averaged?
All agents play in cooperation with other agents including the "keyboard AI"?
Is the keyboard AI controlled by human beings?
Can we assume it plays perfectly well?}}
\paragraph*{\textit{Please cite something about (1+1)-ES}}
\paragraph*{\textit{If all information is visible to the agents,
this problem domain seems not so interesting especially if
both agents are the same.}}
\paragraph*{\textit{I don't think GA is suitable for this domain.
Comparing against A* search with a simple evaluation function would be more interesting.}}

\paragraph*{\textit{"Doors are rendered in Black." -> "Walls are rendered in Black."}}
We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
\subsection{Review 4 (Reviewer B)}
\paragraph*{\textit{there is some mixup with agents being labeled 0 and 1 in the figures, but 1 and 2 in the text.}}

### 2015-08-04 Report/ceec.tex
Dealt with the MCTS terminology issues

\subsubsection{\gls{ai} Controllers}
A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
\paragraph{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\paragraph{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\paragraph{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (from 1-3 to 500-600 in 40ms \footnote{Intel Core i5-3570, 8GB RAM, Windows 7 Enterprise 64bit}). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.

For the tournament, three parameter sets were chosen for comparison and are shown in Figure \ref{mctsTable}.
\begin{figure}[h]
\centering
\begin{tabular}{| l | c | c | c |}
\hline
\textbf{Budget} & \textbf{Iterations} & \textbf{Max UCT} & \textbf{Max Rollout} \\
\hline
Small & 75 & 3 & 15 \\
Medium & 200 & 5 & 30 \\
High & 500 & 10 & 45 \\
\hline
\end{tabular}
\caption{Table of parameters for the 3 \gls{mcts} players}
\label{mctsTable}
\end{figure}

>>>>

\subsubsection{\gls{ai} Controllers}
A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
\paragraph{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\paragraph{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\paragraph{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed number of rollouts, \gls{uct} tree search depth limit and rollout border. The rollout border is how far in total, the forward model will be allowed to progress before the game is evaluated. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (from 1-3 to 500-600 in 40ms \footnote{Intel Core i5-3570, 8GB RAM, Windows 7 Enterprise 64bit}). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.

For the tournament, three parameter sets were chosen for comparison and are shown in Figure \ref{mctsTable}.
\begin{figure}[h]
\centering
\begin{tabular}{| l | c | c | c |}
\hline
\textbf{Budget} & \textbf{Rollouts} & \textbf{UCT Search Limit} & \textbf{Rollout Border} \\
\hline
Small & 75 & 3 & 15 \\
Medium & 200 & 5 & 30 \\
High & 500 & 10 & 45 \\
\hline
\end{tabular}
\caption{Table of parameters for the 3 \gls{mcts} players}
\label{mctsTable}
\end{figure}
